Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-06 paper.tex
Finished description of Agent 1 (but not finished improving it)

\lstinputlisting[caption=The action of going \texttt{north}, captionpos=b,
language=Big, label=agent1_north, firstline=108,
lastline=141]{models/agent1.big}

Lastly, we have five actions (four for the directions, and one for
going home). Each of the actions for directions carries three reaction
rules: one for going to an already visited cell, one for visiting a
cell for the first time, and one for visiting a cell for the
first time and finding an object. We will use the rules for going north
in Listing \ref{agent1_north} as an example. When going to an already visited
cell, the \texttt{Agent} simply traverses a link between the \texttt{North} node
of its previous \texttt{Cell} and the corresponding \texttt{South} node. As this
is the only reaction rule for this situation, its probability is $1$. When
going to an unvisited node, we equip an \texttt{Object} with probability $p$.
Regardless of whether that happens or not, the \texttt{Cell} changes its
status from \texttt{Unvisited} to \texttt{Visited}. % TODO: going home now

>>>>

\lstinputlisting[caption=The action of going north, captionpos=b,
language=Big, label=agent1_north, firstline=108,
lastline=141]{models/agent1.big}

Lastly, we have five actions (four for the directions, and one for
going home). Each of the actions for directions carries three reaction
rules: one for going to an already visited cell, one for visiting a
cell for the first time, and one for visiting a cell for the
first time and finding an object. We will use the rules for going north
in Listing \ref{agent1_north} as an example. When going to an already visited
cell, the \texttt{Agent} simply traverses a link between the \texttt{North} node
of its previous \texttt{Cell} and the corresponding \texttt{South} node. As this
is the only reaction rule for this situation, its probability is $1$. When
going to an unvisited node, we equip an \texttt{Object} with probability $p$.
Regardless of whether that happens or not, the \texttt{Cell} changes its
link from \texttt{Unvisited} to \texttt{Visited}.

\lstinputlisting[caption=Reaction rule to stay home if a required number of
objects is acquired., captionpos=b, language=Big, label=agent1_home,
firstline=204, lastline=216]{models/agent1.big}

The action \texttt{home} has five reaction rules: going west/south to a
visited/unvisited cell that are just like the rules in Listing
\ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
\texttt{goal}, and a rule to stay home if the goal is satisfied (in Listing
\ref{agent1_home}).
